Automated Synthesis of State-Space Digital Controllers

### 2016-11-19 cav2017/cav2017.tex
comments

Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
\begin{align}
\label{eq:discretization}
\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k\\
y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k 
\end{align}
with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
where \commentib{Are the second parts of equations (5) and (6) really nedded?}
\begin{align}
\label{eq:discretize}
\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s}\\
\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B}\\
\vec{C}_d &= \vec{C}\\
\vec{D}_d &= \vec{D} \\
Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt
\end{align}
and $T_s$ is the sample time. Then
\begin{align*}
x(kT)=x_k \wedge y(kT) = y_k, \forall k
\end{align*}
Similarly, we can now state that the Z-transform of the discrete-time equation g(k) and the Laplace transform of the continuous time
equation g(t) are related.
$$g(t) \rightarrow g(k) \Leftrightarrow G(S)=\mathcal{L}(g(t)) \rightarrow G(Z)=\mathcal{Z}(g(k))$$ \commentib{The notation is wrong. There is no implications ($\rightarrow$) between functions.}
where the poles $\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in G(Z) \wedge \lambda_i \in G(S)$ \commentib{This notation is wrong. G(s) (lowercase 's' and not S) is a function in the complex frequency domain, it is not a set. Consequently, the set membership notation $\in$ cannot be employed. } are derived from \eqref{eq:discretize}.
Two remarks are worth mentioning regarding the above.
\begin{remark} 
The above statement is only valid if the sampling frequency is above the Nyquist criteria, since aliasing could cause 'phantom poles' to appear otherwise. 
\end{remark}
\begin{remark}
The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
This means that reasoning about the statespace must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
\end{remark}
Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:dynamical}, we may use the semantics in section \ref{sec:model_semantics} 
to model continuous dynamical systems.

>>>>

Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
\begin{align}
\label{eq:discretization}
\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k\\
y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k 
\end{align}
with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
where \commentib{Are the second parts of equations (5) and (6) really nedded?}
\begin{align}
\label{eq:discretize}
\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s}\\
\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B}\\
\vec{C}_d &= \vec{C}\\
\vec{D}_d &= \vec{D} \\
Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt
\end{align}
and $T_s$ is the sample time. Then
\begin{align*}
x(kT)=x_k \wedge y(kT) = y_k, \forall k
\end{align*}
Similarly, we can now state that the Z-transform of the discrete-time equation g(k) and the Laplace transform of the continuous time
equation g(t) are related.
$$g(t) \rightarrow g(k) \Leftrightarrow G(S)=\mathcal{L}(g(t)) \rightarrow G(Z)=\mathcal{Z}(g(k))$$ \commentib{The notation is wrong. There is no implications ($\rightarrow$) between functions. The discretization process is not a transition system. And this symbol is employed for transformation, but in respect to the domain and counterdomain.}
where the poles $\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in G(Z) \wedge \lambda_i \in G(S)$ \commentib{This notation is wrong. G(s) (lowercase 's' and not S) is a function in the complex frequency domain, it is not a set. Consequently, the set membership notation $\in$ cannot be employed. It is valid for G(z) too. } are derived from \eqref{eq:discretize}.
Two remarks are worth mentioning regarding the above.
\begin{remark} 
The above statement is only valid if the sampling frequency is above the Nyquist criteria, since aliasing could cause 'phantom poles' to appear otherwise. 
\end{remark}
\begin{remark}
The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
This means that reasoning about the statespace must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
\end{remark}
Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:dynamical}, we may use the semantics in section \ref{sec:model_semantics} 
to model continuous dynamical systems.
